### 2024-05-18 fantasy-football.qmd
20240518 - table column widths

@@

@@

@@

>>>>

: Common Scoring Settings for Offensive Players {#tbl-scoringOffense tbl-colwidths="[50,50]"}

@@

: Common Scoring Settings for Kickers {#tbl-scoringKickers tbl-colwidths="[50,50]"}

@@

: Common Scoring Settings for Team Defense/Special Teams {#tbl-scoringDST tbl-colwidths="[50,50]"}

@@

: Common Scoring Settings for Individual Defensive Players {#tbl-scoringIDP tbl-colwidths="[50,50]"}
